\mytitle

### 2020-04-08 paper.tex
commit.
removed log and gz

To 
maximize $f(x)$ and satisfy the total number of turbines and proximity 
constraints we write
the following quadratic optimization problem (QCOP):
\begin{eqnarray} \label{QCOP}
&\max_{x_i}^{}& \sum_{i \in \mathcal{N}}^{} \sum_{d \in \mathcal{D}}^{} p_d ( \frac{1}{3} \ u_{id, \infty}^3 x_i  - \sum_{j \in \mathcal{U}_{id}}^{} \frac{1}{3}(u_{id, \infty} ^3 - u_{ijd}^3)x_i x_j)   \\
&s.t.:& \nonumber\\
&\mbox{       }& \sum_{i \in \mathcal{N}}^{} x_i = m,\label{Cardinality}\\
&\mbox{       }& x_i + x_j \leq 1,   \forall (i,j) \in \mathcal{E}, \label{Grid}\\
&\mbox{       }& x_i \in \{0,1\},     \forall i \in \mathcal{N}.
\end{eqnarray} Constraints~\ref{Cardinality} ensure that exactly $m$ turbines are placed on the grid, while~\ref{Grid}
enforce proximity constraints between the turbines.

@@

>>>>

To 
maximize $f(x)$ and satisfy the total number of turbines and proximity 
constraints we write
the following quadratic optimization problem (QCOP):
\begin{eqnarray} \label{QCOP}
&\max_{x_i}^{}& \sum_{i \in \mathcal{N}}^{} \sum_{d \in \mathcal{D}}^{} p_d ( \frac{1}{3} \ u_{id, \infty}^3 x_i  - \sum_{j \in \mathcal{U}_{id}}^{} \frac{1}{3}(u_{id, \infty} ^3 - u_{ijd}^3)x_i x_j)   \\
&s.t.:& \nonumber\\
&\mbox{       }& \sum_{i \in \mathcal{N}}^{} x_i = m,\label{Cardinality}\\
&\mbox{       }& x_i + x_j \leq 1,   \forall (i,j) \in \mathcal{E}, \label{Grid}\\
&\mbox{       }& x_i \in \{0,1\},     \forall i \in \mathcal{N}.
\end{eqnarray} Constraint~\ref{Cardinality} and \ref{Grid} ensure that exactly $m$ turbines are placed on the grid
and enforce proximity constraints between the turbines, respectively.

@@

\subsubsection{QCOP solving methods}

\todo{Jason's part}

\subsubsection{Specialized Hardware for QUBO}

\todo{Eldan's part}
